\chapter{Concepts and Terminology}
Before we begin, it is important to establish some terminology, which will form a through-line through the rulebook.

\begin{description}
\item[Action] One of the things you can do in a turn.
\item[Action Point (AP)] Something you spend to perform actions. Once out of AP, no more actions can be performed on your turn.
\item[Act] One part of the game. The game is divided into three acts. At the end of the third act, the coach with the most points wins the game.
\item[Coach] You, the person playing the game.
\item[Player] A player is one of the movable models.
The players have different stats as outlined by the Teams chapter.
\item[Field] The main play area of the game board. The field is lined with hexes, lines, and numbers. The numbers are purely æsthetic to evoke the idea of football pitch yard lines.
\item[Capture Zone] Each team has a capture zone.
The capture zone is where the flags and ball are brought in order to score points for a round.
\item[Fate Die] A die which has \plus{}, \minus{}, and \blank{} on its faces rather than pips/numbers.
In most instances, this will be treated as a $\pm 1$ or a 0 for stats.
\item[dF] Dice notation for a \textit{Fate Die}. 
$3dF$ refers to rolling 3 \fate{} dice, $2dF+1$ means ``roll two \fate{} dice and add 1 to the result''
\item[Skill Check] Comparing a player's skill and rolling a \fate{} die.
\item[Scatter Die] A scatter die is a die with four arrows and two hits on it. When rolled, the arrows randomly choose a direction, but there's also a chance to hit.
\item[Team] Your personal selection of player models.
\end{description}