\chapter{The Game}
\section{Basic Gameplay} \label{basic-gameplay}
The objective of the game is to score the most points by capturing the opponents' flags while keeping your own safe.
A game is broken down in the following way:
\begin{enumerate}
    \item A game consists of three acts, called Thirds.
    These work similar to half-times in most sports.
    % TODO: Find a way to possibly automate this
    \item The game starts with rock-paper-scissors, dice roll, or other means to determine who goes first.
    % TODO: introduce a play-book mechanic
    \item Each coach starts a Third by positioning their players on their side of the board.
    Coaches place all their players all at once, starting with the first coach.
    \item The first coach in the turn order places their flag anywhere within the centre zone.
    \item The other coaches roll 4dF+3, counting all non-\blank{} as \plus{}'s. The first coatch's flag is then moved that number of hexes within the centre zone.
    It is up to the other coaches to decide amongst themselves who gets to do this.
    \item The remaining coaches place their flag on the T in their Capture Zone.
    \item Once a coach is done positioning their players, they may not try and reposition them in response to the placement of the other teams' players.
    \item On their turn, a player may:
    \begin{enumerate}
        \item Do nothing.
        \item Move a number of hexes less than or equal to their move score.
        \item Harm, Shove, or Dodge an opponent (see Section \ref{skill-checks}).
        \item A special action, which may require Source (see Section \ref{energy}).
        \item Pass \ball{} and/or throw a \flag{} (see Section \ref{flag-interaction})
    \end{enumerate}
    \item A \flag{} or \ball{} is picked up automatically upon touching, unless it’s either thrown at you or rolling towards you (see Section \ref{flag-interaction}).
    \item A Third ends when \ball{} is captured.
\end{enumerate}

\input{chapters/the-game/the-team.tex}
\input{chapters/the-game/skill-checks.tex}
\input{chapters/the-game/moving.tex}
%\input{chapters/the-game/energy.tex}
\section{Specials \& Source}\label{energy}
TBD
\input{chapters/the-game/flag-interaction.tex}
\input{chapters/the-game/scoring.tex}