\chapter{The Game}
\section{Basic Gameplay} \label{basic-gameplay}
\begin{enumerate}
    \item A game consists of three acts, called Thirds. These work similar to half-times in most sports.
    \item The game starts with rock-paper-scissors, dice roll, or other means to determine who goes first.
    \item Each player starts a Third by positioning their units on their side of the board. Positioning units goes clockwise around the board, starting with the first player. 
    \item Once a player is done positioning their units, they may not try and reposition them in response to the placement of the other teams’ units.
    \item A character can do one of four things on its turn:
    \begin{enumerate}
        \item Do nothing.
        \item Move a number of hexes less than or equal to their move score.
        \item Attack an opponent (see Section \ref{attacking}).
        \item Throw or Pass a flag (see Section \ref{flag-interaction})
    \end{enumerate}
    \item A special action is permitted once per player per turn (see Section \ref{special-action}).
    \item A flag is picked up automatically upon touching, unless it’s either thrown at you or rolling towards you (see Section \ref{flag-interaction}).
\end{enumerate}

\input{chapters/the-game/the-team.tex}
\input{chapters/the-game/skill-rolls.tex}
\input{chapters/the-game/moving.tex}
\input{chapters/the-game/attacking.tex}
\input{chapters/the-game/energy.tex}
%\input{the-game/throwing-passing.tex}
%\input{the-game/special-action.tex}
\input{chapters/the-game/flag-interaction.tex}
\input{chapters/the-game/scoring.tex}